---
title: "p8105_hw1_yc4585"
output: html_document
date: "2024-09-12"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load dataset
```{r load data, results='hide'}
  data("penguins", package = "palmerpenguins")
  str(penguins)
  nrow(penguins)
  ncol(penguins)
  number_mean = mean(penguins$flipper_length_mm, na.rm = TRUE)
  
```
        
  The the main variables in the dataset include species,island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex and year.


  The dataset have `r nrow(penguins)` rows and `r ncol(penguins)` columns, the mean of flipper length is `r number_mean`.

## Make sactterplot
```{r scatterplot, warning=FALSE}
library(ggplot2)
plot_data = data.frame(
  x = penguins$bill_length_mm,
  y = penguins$flipper_length_mm
)

ggplot(plot_data, aes(x=x, y=y, colour = penguins$species)) + 
  geom_point() +
  labs(x = "Bill Length (mm)", y = "Flipper Length (mm)")

ggsave(
  filename = "penguins.png", 
  width = 7,                     
  height = 7,                    
  units = "in",                   
  dpi = 600                      
)
```


You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
