---
title: "p8105_hw1_yc4585"
output: github_document
date: "2024-09-12"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Problem 1
### Load dataset
```{r load data, results='hide'}
  data("penguins", package = "palmerpenguins")
  str(penguins)
  nrow(penguins)
  ncol(penguins)
  number_mean = mean(penguins$flipper_length_mm, na.rm = TRUE)
  
```
        
  The the main variables in the dataset include species,island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex and year.


  The dataset have `r nrow(penguins)` rows and `r ncol(penguins)` columns, the mean of flipper length is `r number_mean`.

### Draw sactterplot
```{r scatterplot, warning=FALSE}
library(ggplot2)
plot_data = data.frame(
  x = penguins$bill_length_mm,
  y = penguins$flipper_length_mm
)

ggplot(plot_data, aes(x=x, y=y, colour = penguins$species)) + 
  geom_point() +
  labs(x = "Bill Length (mm)", y = "Flipper Length (mm)")

ggsave(
  filename = "penguins.png", 
  width = 7,                     
  height = 7,                    
  units = "in",                   
  dpi = 600                      
)
```
## Problem 2
```{r loading tidyverse, message=FALSE}
  library(tidyverse)
```

```{r creat data frame}
  vec_numeric = rnorm(10,0,1)
  vec_logical = vec_numeric > 0
  vec_character = vector("character", length = 10)
  pre_factor = c("A", "A", "A", "A", "A", "A", "B", "B", "C", "C")
  vec_factor = factor(pre_factor, levels = c("A", "B", "C"))
  my_data = data.frame(
    vec_numeric ,
    vec_logical ,
    vec_character ,
    vec_factor )
  print(my_data)
```
The code above show the required data frame.

```{r}
Vec_Numeric = my_data %>% pull(vec_numeric)
mean(Vec_Numeric)
Vec_Logical = my_data %>% pull(vec_logical)
mean(Vec_Logical)
Vec_Character = my_data %>% pull(vec_character)
mean(Vec_Character)
Vec_Factor = my_data %>% pull(vec_factor)
mean(Vec_Factor)
```
We can calculate the mean of numeric vector and logical vector, but we cannot calculate the mean of character vector and factor vector.

```{r conver variable types,results='hide'}
num_logical = as.numeric(Vec_Logical)
num_character = as.numeric(Vec_Character)
num_factor = as.numeric(Vec_Factor)
```



